Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
fig 7 caption

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, either manually corrected or raw from Pero-OCR and Tesseract. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{reference}$). Results show that best performances on noisy entries are obtained when the model has been pre-trained and fine-tuned for NER on examples affected with a similar OCR noise.}
    \label{fig:exp_2_eval_ner}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{reference}$).  Results show that best performances on noisy entries are obtained when the model has been pre-trained and fine-tuned for NER on examples affected with a similar OCR noise.}
\end{figure}
